The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
add pkg citations

Code for performing all multilayer social network analyses and generating the
figures is available at 
https://github.com/robitalec/scale-in-multilayer-networks [@Robitaille_2020] <!-- TODO: zenodo-->
and released under the GNU General Public License 3.0. We depended on numerous R
packages notably for the analysis: igraph, data.table, spatsoc, asnipe, and
grainchanger, for the figures: ggplot2 and patchwork, and for reproducibility
and workflow management drake, renv, and knitr.

>>>>

Code for performing all multilayer social network analyses and generating the
figures is available at https://github.com/robitalec/scale-in-multilayer-networks 
[@Robitaille_2020] and released under the GNU General Public License 3.0. 
We depend on numerous R packages notably for the analysis: `igraph` [@Csardi_2006],
`data.table` [@Dowle_2019], `spatsoc` [@Robitaille_2019], `asnipe` [@Farine_2019],
and `grainchanger` [@Graham_2019], for the figures: `ggplot2` [@Wickham_2016] and
`patchwork` [@Pedersen_2019], and for reproducibility and workflow management: 
`drake` [@Landau_2018], `renv` [@Ushey_2020], and `knitr` [@Xie_2015].
